\section{\whoscoredplain}

\whoscored\ is a football statistics web site, offering free statistics for almost 500 different leagues and tournaments all over the world (as of \today). Their database is vast, covering matches all the way back to 1999 for some competitions.

\subsection{Match statistics}

\whoscored\  offers match statistics on three different levels of details; minimum, intermediate, and full.

\subsubsection{Minimum details}

For matches with minimum available details, only the basic information is available; what teams are playing, time elapsed, final result, and kickoff time. The majority of all competitions fall into this category.

\subsubsection{Intermediate details}

For matches with intermediate details, some additional information is included in addition to the basic information; lineups, substitutes, and the most important match events (goals, penalty misses, substitutions, and red and yellow cards).

This was the most detailed level of details from August 2002 throughout the season 2008/2009.

\subsubsection{Full details}
\label{subsubsec:whoscored-full-details}

Only a handful of competitions are covered with full match details. In addition to the most basic information, the full details include generic information about the match, such as venue, attendance number, referee, weather conditions, and team managers.

The full details also include a detailed overview of almost all events taking place during the match. Free kicks, tackles, saves, and passes are examples of such events. Each event has several properties, such as location on the pitch, at what time it happened, and players involved. A thorough description of the detailed match data is included in \referappendix{chp:whoscored-data-description}.

In addition to event data, the full details contain information about the teams' formations; each formation the team used during the match, with player positions, who was captain, and when the formation started and ended.

The full details also include statistics for each participating player. The statistics consist of several metrics, such as the number of tackles, saves, or passes, and how they developed over time. A list of all available metrics is included in \refertable{tab:whoscored-player-metrics}.

Lastly, the full details include ratings of all involved players, along with a rating for the team as a whole. The ratings are valued on a scale from 0 through 10, where 10 is the top rating. The ratings are calculated based on the player's contribution to the team.


\subsection{Team and player statistics}

\whoscored\ also offers team and player statistics. Descriptions of the statistics are shown in \refertable{tab:whoscored-team-views} and \refertable{tab:whoscored-player-views}.