\section{Report outline}

This section presents the outline of the rest of the report.

\begin{itemize}
    \item \textbf{\cref{chp:background}} presents the background research conducted before starting the work in this report. Firstly, a state of the art assessment concerning football match prediction and betting is presented. Then, relevant technologies are presented. Lastly, an overview of the data available at \whoscored\ is presented.
        
    \item \textbf{\cref{chp:theory}} presents the theory needed in order to understand the contents of this report. The theory behind statistical classification and \glspl{ann} is presented. 

    \item \textbf{\cref{chp:system-architecture}} presents the architecture of the software system built for the experiments in this report. Firstly, an overview of the database used is presented. Then, the scraper used when scraping \whoscored\ for data is presented. Lastly, the betting simulator constructed in order to test the prediction models in a betting setting is presented.

    \item \textbf{\cref{chp:experimental-setup}} presents the setup for the experiments conducted in this report. Firstly, a summary of the different prediction models is presented. Then, the betting simulation procedure is presented.

    \item \textbf{\cref{chp:experiments-results}} presents the experiments conducted and results achieved in this report.

    \item \textbf{\cref{chp:conclusion-future-work}} presents a conclusion and discussion of the results achieved during the experiments, along with the author's thoughts on where to go from now. The author first reflects on how accepting different kinds of bets will affect the profitability of the networks. Then, thoughts on including different variables are presented. Lastly, a potential improvement to the data collection system is presented.
\end{itemize}